---
params:
  system: "all"
  analyst_mode: FALSE
title: "System Metrics Reference Guide"
author: "Ewan Wakeman"
date: "02/12/2020"
output: 
  md_document:
    variant: markdown_github
---

```{r setup, include=params$analyst_mode, warning=FALSE, message=FALSE, echo=FALSE}


# Set Parameters
knitr::opts_chunk$set(echo = params$analyst_mode, message=FALSE, warning = FALSE, root.dir = normalizePath(".."))
root <- knitr::opts_chunk$get('root.dir')

# Set directory for markdown chunks of text and function to display them
md_dir <- file.path(root, 'markdown')
md <- function(file){includeMarkdown(paste(md_dir, file, sep='/'))}

# Load Packages
req_pack <- c('htmltools', 'tidyverse', 'sf', 'knitr', 'glue', 'lubridate', 'patchwork', 'knitr')
invisible(sapply(req_pack, require, character.only=T, quietly=T))

# Load Associated themes / plotting functions
list.files(file.path(root, 'theme'), '\\.[Rr]', full.names = T) %>% map(source)
source(file.path(root,'/R/metadata.r'))
source(file.path(root, '/R/plotting.r'))
theme_set(thm$theme_light())

# list ind codes
inds <- get_indicators(path = file.path(root, '/data/system_metrics_indicator_list.csv'))
# Load data
smd <- read_csv(file.path(root, 'data/sys_metrics.csv'))

# Set up params
all_sys <-
  smd %>%
  group_by(stp_code, stp_name) %>%
  summarise()

if (params$system %in% all_sys$stp_code){
  sys <- with(all_sys[all_sys$stp_code == params$system,], 
              list(code = stp_code, name = stp_name))
} else if (params$system %in% all_sys$stp_name){
  sys <- with(all_sys[all_sys$stp_name == params$system,], 
              list(code = stp_code, name = stp_name))
} else if (params$system == 'all'){
  sys <- list(code = 'all', name = 'national')
} else {
  warning('System name or code not found in data!')
  sys <- list(code = NA, name = NA)
}

smd_grp <-
  smd %>%
  ungroup() %>%
  filter(ind_code %in% inds,
         year(period_start) >= 2010,
         val > 0) %>%
  group_by(ind_code, ind_name,
           period_start, period_end) %>%
  summarise(
    'count' = n(),
    'mean' = mean(val, na.rm =T),
    'sd' = sd(val, na.rm = T),
    'se' = sd/sqrt(count),
    .groups = 'drop'
  ) 

smd_nest <-
  smd_grp %>%
  group_by(ind_code, ind_name) %>%
  nest() %>%
  ungroup()
```

# Introduction
```{r intro}
md('intro.md')
sys_metrics_tab <- read_csv(file.path(root, 'data/system_metrics_tab.csv'))
kable(sys_metrics_tab)
```
# Metrics

## Are systems delivering better, more equal  outcomes to the people who live there?

```{r outcome-metrics-md}
md('outcome_metrics.md')
```
#### Visualation over time

```{r outcomes-plots, fig.height=10, fig.width=8}
outcomes <- c('hle_0', 'cvmcp')
plots <-
  smd_nest %>%
  filter(ind_code %in% outcomes) %>%
  unname() %>%
  pmap(time_series_plot)

(plots[[1]] / plots[[2]])
```


```{r working-together-md}
md('working_together.md')
```

#### Visualisation over time

```{r working-together-vis}
work_tog <- c('av_adm')
plots <-
  smd_nest %>%
  filter(ind_code %in% work_tog) %>%
  unname() %>%
  pmap(time_series_plot)

plots[[1]]
```

```{r prevention-md}
md('prevention.md')
```

#### Visualisation over time

```{r prevention-vis}
prev <- c('phys_act', 'obs_y6')
plots <-
  smd_nest %>%
  filter(ind_code %in% prev) %>%
  unname() %>%
  pmap(time_series_plot)

plots[[1]]
```


```{r staff-support-md}
md('staff_support.md')
```

#### Visualisation over time

```{r staff-viz, fig.width=12}
staff <- c("pc_gp_ratio", "pc_nurse_ratio",  "sc_nurse_ratio", "sc_doc_ratio", "asc_directcare_ratio")
filtered <-
  smd %>%
  filter(ind_code %in% staff)
pc_sc_plot(filtered)
```

```{r finances}
md('finances.md')
```

# Principles

```{r principles}
md('open_source.md')
md('principles.md')
```

# Important Concepts

## Time Series and Trends

```{r time-series}
md('time_series.md')
```

## Geographical Variation

```{r geo-variation}
md('geo_variation.md')
```

## Relationships between metrics

```{r relationships}
md('metric_relationships.md')
```

## Demographic data
```{r demography}
md('demography.md')
```

# Visualisation of Data

# Links to other work

